A Review on Multi-Label Learning Algorithms

### 2018-01-16 Paper/Presentation/mll_review.tex
update presentation
Update presentation

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
\item[$\bullet$] Transform into a label pairwise comparison ranking problem
\item[$\bullet$] For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison and use a binary algorithm $g_{jk}(x)$
\item[$\bullet$] Construct training sets $D_{jk} : \{x_i, Y_i | y_j \in Y_i \oplus y_k \in Y_i\}$. System votes for each example and if $g_{jk}(x) >0$,$x_i$ is associated with $y_j$, otherwise with $y_k$
\item[$\bullet$] For an unknown instance, all classifiers' votes are aggregated and ranked
\item[$\bullet$] A virtual label $y_v$ serves as the artificial splitting point between relevant and irrelevant labels
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach algorithm. One-vs-one scheme.
\item[$\bullet$] Smooths out the class-imbalance problem
\item[$\bullet$] Number of classifiers s quadratic to $|Y|$ (compared to linear for BR)
\begin{itemize}
\item[$\circ$] Pruning methods to reduce the search space
\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
\item[$\bullet$] Decompose to an ensemble of multi-class classification problems
\item[$\bullet$] Each component targets a random subset of $\mathbb{P}(Y)$ that appears in $X$, classified with Label Powerset (LP) techniques:
\begin{itemize}
\item[$\circ$] Transform to single-label data by treating each distinct labelset as a new class
\item[$\circ$] Each example is reassigned with the new mapped class and classified through regular single-label classification
\item[$\circ$] M-L classify $x$ with $y_i$ when the votes received for $y_i$ from the ensemble exceed half the max possible it can get
\end{itemize}
todo how does each LP classify, k-labelsets
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] High-order approach algorithm
\item[$\bullet$] Data-sensitive: Cannot generalize to labelsets not in the training set, too few examples for some labelsets
\item[$\bullet$] Large $Y$ implies high training complexity.
\item[$\bullet$] Improve by invoking an ensemble on random k-sized labelsets
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Algorithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.75]{images/aa.png}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
\item[$\bullet$] First-order approach algorithm, adapting knn techniques
\item[$\bullet$] Compares the MAP probabilities: $P(K|C_j), K \in \{H_j, \neg H_j\}$
\item[$\bullet$] Priors $P(K)$ computed by smoothed frequency estimation in the training data
\item[$\bullet$] Likelihoods $P(C_j|K)$ are computed as a function of:
\begin{itemize}
\item[$\circ$] $\kappa(r)$, the number of examples labelled $y_j$ with $r$ neighbours labelled $y_j$
\item[$\circ$] $\overset{\sim}{\kappa}(r)$, the number of examples not labelled $y_j$ with $r$ neighbours labelled $y_j$
\end{itemize}
\end{itemize}

Pros \& cons:
\begin{itemize}
\item[$\bullet$] First-order approach, Bayesian and Lazy reasoning
\item[$\bullet$] Decision boundary can be modified on-line via new instances
\item[$\bullet$] Class imbalance can be overcome by calculating priors
\item[$\bullet$] Extensions proposed for label correlation exploitations
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}
\begin{itemize}
\item[$\bullet$] Multi-label entropy is used to build a decision tree recursively
\item[$\bullet$] Split position is such that the information gain criterion is maximized
\item[$\bullet$] Dataset $T$ is split on the $l$-th feature valued $\theta$ to branches ($T^-$ \& $T^+$), where $ x_{il} \leq \theta, x_i \in T^-$ and $ x_{il} > \theta, x_i \in T^+$
\item[$\bullet$] Recurse on subtrees until a stopping criterion is met (e.g. child size)
\item[$\bullet$] Single-label entropy is computed by considering labelsets as new classes
\item[$\bullet$] Assumes independence among labels to ensure low computational cost
\item[$\bullet$] Unseen instances are assigned the label of the majority of members of the leaf they arrive
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] First-order algorithm, highly efficient
\item[$\bullet$] Assumes label independence
\item[$\bullet$] Pruning and ensemble strategies proposed
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}
\begin{itemize}
\item[$\bullet$] $q$ linear classifiers, optimized to minimize the empirical ranking loss
\item[$\bullet$] For each relevant-nonrelevant label pair $(y_j,y_k) \in Y_j \times \bar Y$ their decision boundary is marked by $\left<w_j,w_k\right> + b_j - b_k=0$
\item[$\bullet$] Retrieves a ranked label pairs list for each unseen instance
\item[$\bullet$] Non-linearity achievable through feature mapping and the kernel trick
\item[$\bullet$] Convex quadratic programming problem, solved by any QP solver
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach, maximum margin strategy
\item[$\bullet$] Extensible by kernel learning, kernel selection can be overcome by MKL techniques
\item[$\bullet$] Adaptable learning by selecting an appropriate loss function
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}
\begin{itemize}
\item[$\bullet$] Labels encoded as binary random vectors into a joint pdf
\item[$\bullet$] Label correlations encoded into the joint pdf as constraints
\item[$\bullet$] Model via the maximum information entropy criterion: $H_p(x, y)$, subject to constraints $\mathbb{E_p}[f_k(x,y)] = F_k$, where $F_k$ are estimated from the training set
\item[$\bullet$] Objective arrived by Lagrange multipliers, solvable by any constraint optimization solver
\item[$\bullet$] Unseen instances labelled with $Y = \underset{y}{\text{argmax }} P(y | x)$
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach. All label pairs considered, not just relevant-irrelevant ones.
\item[$\bullet$] Intractable $\text{argmax}$ operation for a large label space without pruning.
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : Summary}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.45]{images/summary.png}
\caption{Summary of Representative Multi-Label Learning Algorithms}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
\item[$\bullet$] Multi-instance learning
\begin{itemize}
\item[$\circ$] Each ML example described by a bag of instances while associated with a single/binary label
\item[$\circ$] Models the object’s complex semantics in input space, rather than its output
\end{itemize}
\item[$\bullet$] Ordinal classification
\begin{itemize}
\item[$\circ$] Model class co-relevance in a (vague) graded membership vector
\item[$\circ$] Transform ML problem to a set of ordinal set of problems
\end{itemize}
\item[$\bullet$] Multi-task learning
\begin{itemize}
\item[$\circ$] Multiple tasks trained in parallel, sharing information
\item[$\circ$] Knowledge from related tasks used as an inductive bias to improve generalization
\item[$\circ$] Shared or different feature space, small task workload
\end{itemize}
\item[$\bullet$] Data streams classification
\begin{itemize}
\item[$\circ$] Real-world objects are generated online and processed in  real-time
\item[$\circ$] Concept drift problem
\end{itemize}
\end{itemize}
\end{frame}

%------------------------------------------------
\section{Conclusion}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Conclusion}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : Online resources}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.47]{images/online.png}
\caption{Online Resources for Multi-Label Learning}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
Summary:
\begin{itemize}
\item[$\bullet$] Multi-label learning problem definition
\item[$\bullet$] Multi-label learning representative algorithms
\item[$\bullet$] Related learning settings
\end{itemize}

@@

%------------------------------------------------
\subsection{Related Work}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{itemize}
\item[$\bullet$] Madjarov, Gjorgji, et al. "An extensive experimental comparison of methods for multi-label learning." Pattern Recognition 45.9 (2012): 3084-3104
\item[$\bullet$] Tsoumakas, Grigorios, and Ioannis Katakis. "Multi-label classification: An overview." International Journal of Data Warehousing and Mining 3.3 (2006)
\item[$\bullet$] Zhang, Min-Ling, and Kun Zhang. "Multi-label learning by exploiting label dependency." Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010
\end{itemize}
\end{frame}

>>>>

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
\item[$\bullet$] Transform into a label pairwise comparison ranking problem
\item[$\bullet$] For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison and use a binary algorithm $g_{jk}(x)$
\item[$\bullet$] Construct training sets $D_{jk} : \{x_i, Y_i | y_j \in Y_i \oplus y_k \in Y_i\}$. System votes for each example and if $g_{jk}(x) >0$,$x_i$ is associated with $y_j$, otherwise with $y_k$
\item[$\bullet$] For an unknown instance, all classifiers' votes are aggregated and ranked
\item[$\bullet$] A virtual label $y_v$ serves as the artificial splitting point between relevant and irrelevant labels
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach algorithm. One-vs-one scheme.
\item[$\bullet$] Smooths out the class-imbalance problem
\item[$\bullet$] Number of classifiers s quadratic to $|Y|$ (compared to linear for BR)
\begin{itemize}
\item[$\circ$] Pruning methods to reduce the search space
\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
\item[$\bullet$] Decompose to an ensemble of multi-class classification problems
\item[$\bullet$] Each component targets a random subset of $\mathbb{P}(Y)$ that appears in $X$, classified with Label Powerset (LP) techniques:
\begin{itemize}
\item[$\circ$] Transform to single-label data by treating each distinct labelset as a new class
\item[$\circ$] Each example is reassigned with the new mapped class and classified through regular single-label classification
\item[$\circ$] M-L classify $x$ with $y_i$ when the votes received for $y_i$ from the ensemble exceed half the max possible it can get
\end{itemize}
todo how does each LP classify, k-labelsets
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] High-order approach algorithm
\item[$\bullet$] Data-sensitive: Cannot generalize to labelsets not in the training set, too few examples for some labelsets
\item[$\bullet$] Large $Y$ implies high training complexity.
\item[$\bullet$] Improve by invoking an ensemble on random k-sized labelsets
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Algorithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.75]{images/aa.png}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
	\item[$\bullet$] Let $H_j \equiv (y_j \in Y_i)$, $C_j = \sum_{x_k \in N(x_i)} [\delta(y_j \in Y_k)]$
\item[$\bullet$] Compares the MAP probabilities: $P(K|C_j), K \in \{H_j, \neg H_j\}$ to decide if to include $y_j$ in the prediction. Compute with the Bayes' theorem.
\item[$\bullet$] Priors $P(K)$ computed by smoothed frequency counting in the training data
\item[$\bullet$] Likelihoods $P(C_j|K)$ are computed as a function of:
\begin{itemize}
\item[$\circ$] $\kappa(r)$, the number of examples labelled $y_j$ with $r$ neighbours labelled $y_j$
\item[$\circ$] $\overset{\sim}{\kappa}(r)$, the number of examples not labelled $y_j$ with $r$ neighbours labelled $y_j$
\end{itemize}
\end{itemize}

Pros \& cons:
\begin{itemize}
\item[$\bullet$] First-order approach, Bayesian reasoning
\item[$\bullet$] Decision boundary can be modified on-line via new instances
\item[$\bullet$] Class imbalance can be overcome by calculating priors
\item[$\bullet$] Extensions proposed for label correlation exploitations
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}
\begin{itemize}
\item[$\bullet$] Multi-label entropy is used to build a decision tree recursively
\item[$\bullet$] Split $x$ at feature $l$ s.t. the information gain criterion is maximized
\item[$\bullet$] Dataset $T$ is split on the $l$-th feature valued $\theta$ to branches ($T^-$ \& $T^+$), where $ x_{il} \leq \theta, x_i \in T^-$ and $ x_{il} > \theta, x_i \in T^+$
\item[$\bullet$] Recurse on subtrees until a stopping criterion is met (e.g. child size)
\item[$\bullet$] Single-label entropy is computed by considering labelsets as new classes
\item[$\bullet$] Assumes independence among labels to ensure low computational cost
\item[$\bullet$] Unseen instances are assigned the label of the majority of members of the leaf they arrive
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] First-order algorithm, highly efficient
\item[$\bullet$] Assumes label independence
\item[$\bullet$] Pruning and ensemble strategies proposed
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}
\begin{itemize}
	\item[$\bullet$] $q$ linear classifiers $h_i(x)$, optimized with the empirical ranking loss
\item[$\bullet$] Relevant-nonrelevant label pairs of $x_i$ $(y_j,y_k) \in Y_i \times \bar Y_i$ are separated by a function of their classifiers $h_j, h_k$: $\left<w_j-w_k, x_i \right> + b_j - b_k=0$
\item[$\bullet$] Retrieves a ranked list of label pairs for each unseen instance
\item[$\bullet$] Non-linearity achievable through feature mapping and the kernel trick
\item[$\bullet$] Convex quadratic programming problem, solved by any QP solver
\end{itemize}
TODO : details of operation ixta
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach, maximum margin strategy
\item[$\bullet$] Extensible by kernel learning: kernel selection can be overcome by Multiple Kernel Learning techniques
\item[$\bullet$] Adaptable learning by selecting an appropriate loss function
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}
\begin{itemize}
\item[$\bullet$] Labels encoded as binary random vectors into a joint pdf
\item[$\bullet$] Label correlations encoded into the joint pdf as constraints
\item[$\bullet$] Model via the maximum information entropy criterion: $H_p(x, y)$, subject to constraints $\mathbb{E_p}[f_k(x,y)] = F_k$, where $F_k$ are estimated from the training set
\item[$\bullet$] Objective arrived by Lagrange multipliers, solvable by any constraint optimization solver
\item[$\bullet$] Unseen instances labelled with $Y = \underset{y}{\text{argmax }} P(y | x)$
\end{itemize}
how the fuck
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach. All label pairs considered, not just relevant-irrelevant ones.
\item[$\bullet$] Intractable $\text{argmax}$ operation for a large label space without pruning.
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : Summary}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.45]{images/summary.png}
\caption{Summary of Representative Multi-Label Learning Algorithms}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
\item[$\bullet$] Multi-instance learning Todoooo
\begin{itemize}
\item[$\circ$] Each ML example described by a bag of instances while associated with a single/binary label
\item[$\circ$] Models the object’s complex semantics in input space, rather than its output
\end{itemize}
\item[$\bullet$] Ordinal classification Todoooo
\begin{itemize}
\item[$\circ$] Model class co-relevance in a (vague) graded membership vector
\item[$\circ$] Transform ML problem to a set of ordinal set of problems
\end{itemize}
\item[$\bullet$] Multi-task learning
\begin{itemize}
\item[$\circ$] Multiple tasks trained in parallel, sharing information
\item[$\circ$] Knowledge from related tasks used as an inductive bias to improve generalization
\item[$\circ$] Shared or different feature space, small task workload
\end{itemize}
\item[$\bullet$] Data streams classification
\begin{itemize}
\item[$\circ$] Real-world objects are generated online and processed in  real-time
\item[$\circ$] Concept drift problem
\end{itemize}
\end{itemize}
\end{frame}

%------------------------------------------------
\section{Conclusion}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Conclusion}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
Summary:
\begin{itemize}
\item[$\bullet$] Multi-label learning problem definition
\item[$\bullet$] Multi-label learning representative algorithms
\item[$\bullet$] Related learning settings
\end{itemize}

@@

%------------------------------------------------
\subsection{Online resources}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.47]{images/online.png}
		\caption{Online Resources for Multi-Label Learning}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\subsection{Related Work}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{itemize}
\item[$\bullet$] Madjarov, Gjorgji, et al. "An extensive experimental comparison of methods for multi-label learning." Pattern Recognition 45.9 (2012): 3084-3104
\item[$\bullet$] Tsoumakas, Grigorios, and Ioannis Katakis. "Multi-label classification: An overview." International Journal of Data Warehousing and Mining 3.3 (2006)
\item[$\bullet$] Zhang, Min-Ling, and Kun Zhang. "Multi-label learning by exploiting label dependency." Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010
\end{itemize}
\end{frame}
